Turbo fast no compromise gravitational wave parameter estimation

### 2023-01-10 src/tex/ms.tex
Add paragraph related JSO

>>>>

% Describe the distance between flowMC result and Bilby result using Jensen-Shannon divergence, scipy has a function to compute that in scipy.spatial.distance

For a quantitative comparison between results obtained through our code and other existing tools,
we compute the Jensen-Shannon divergence of the marginalized distribution between our code and \texttt{Bilby}.
The Jensen-Shannon divergence is a symmetric measure of the distance between two probability distributions,
with a value of 0 indicating identical distributions and a value of $\ln{2} \textrm{nat}$ representing
the maximum possible divergence between two distributions.
\kw{Report JSO}
